Limitations on the Two-Infall Scenario in the Era of Large Stellar Age Catalogs

### 2025-04-22 src/tex/ms.tex

An explanation for the $\alpha$-bimodality has yet to be broadly accepted in the GCE community \todo{(reword)}. An $\alpha$-bimodality is not a universal feature in simulated Milky Way-mass galaxies \todo{(citations; also mention external galaxies?)}, so its presence and characteristics in our own galaxy may provide clues to its unique evolutionary history. GCE models that attempt to solve this problem generally fall into two camps: some explain the $\alpha$-bimodality as a result of secular processes, such as the radial migration of stars and the inside-out growth of the disk \todo{(citations)}; others argue that the two sequences point to a bursty star formation history, perhaps driven by multiple discrete accretion events \citep[e.g.,][]{chiappini_chemical_1997,mackereth_origin_2018,spitoni_beyond_2023} or a change in the star formation efficiency \citep[e.g.][]{conroy_birth_2022}.

% Summary of two-infall literature
The two-infall model of chemical evolution was proposed by \citet{chiappini_chemical_1997} to explain the origin of the high- and low-$\alpha$ disks. Though the model has been revised and refined since, the basic premise remains the same: the rate of gas infall onto the Galaxy is described by two consecutive, exponentially declining bursts. The relatively low infall rate between the two bursts leads to a hiatus in the star formation rate, allowing the gas abundance to evolve between the high- and low-$\alpha$ sequences without producing many stars in between. 
% By varying the timescale of the second infall, the model can produce inside-out disk growth and a radial abundance gradient.
The initial model of \citet{chiappini_chemical_1997} successfully reproduced the available abundance data at the time, which were largely confined to the Solar neighborhood.

@@

% \todo{Observational evidence other than $\alpha$-bimodality.} 
The chemical and kinematic separation of the high- and low-$\alpha$ disks remains the primary observational evidence behind the two-infall model. \citet{spitoni_remind_2024} argued that the gap between the sequences in \aFe, contrasted with their overlap in $[\alpha/{\rm H}]$, supports a haitus in star formation which is a natural consequence of the two-infall model. \citet{nissen_high-precision_2020} measured abundances and estimated ages for nearby Solar-type stars and reported two sequences in the age--metallicity distribution which could be explained by the two-infall model \todo{(rewrite)}. \citet{nataf_accurate_2024} also observed multiple sequences in the age--metallicity relation in their sample of $\sim400,000$ local subgiants, although the break between them is not as clean as in \citet{nissen_high-precision_2020}. \citet{chen_recent_2025}, however, argue that this trend can be explained by a smooth star formation history with inside-out growth: the older sequence consists of stars which have migrated from the inner galaxy, where the star formation rate peaked early, while the younger sequence was formed locally.

% \todo{Outflows.} 
Most previous studies of the two-infall model do not include mass-loaded outflows. Some hydrodynamic simulations of Galactic fountains ejected by CC SNe have shown that ejected material falls back onto the disk on relatively short timescales \citep{spitoni_galactic_2008,spitoni_effects_2009} and close to the point of origin \citep{melioli_hydrodynamical_2008,melioli_hydrodynamical_2009}, suggesting the effect on GCE could be minimal. However, other simulations of MW-like galaxies with different feedback prescriptions do produce mass-loaded outflows \todo{(citations)}. Empirically, mass-loaded outflows have been observed in nearby starburst galaxies \todo{(citations)} and dwarf galaxies \todo{(citations)} but not MW-like systems due to current detection limits \todo{(citations)}. We adopt an {\it ad hoc} prescription for outflows as a function of radius in order to balance different yield sets and reproduce the radial metallicity gradient. \todo{Trim down, move some to methods.}

% \todo{Migration.} 
The two-infall model attempts to reproduce the full distribution of stellar abundances in the Solar neighborhood through a single, continuous evolutionary track. \citet{sellwood_radial_2002} first showed that transient spiral perturbations can induce large changes in the guiding radius of a star without kinematic heating. It is now understood that the stars that make up the Solar neighborhood are drawn from a wide range of birth radii \citep[e.g.,][]{schonrich_chemical_2009,frankel_measuring_2018,lehmann_probing_2024}. Some studies have attempted to derive stellar birth radii \citep[e.g.,][]{ratcliffe_unveiling_2023,lu_there_2024}, though such an endeavor requires assumptions about the evolution of the Milky Way's radial metallicity gradient. While the strength and speed of radial migration in the disk are not precisely measured, it is clear that a single chemical evolution track need not explain the entirety of the local observed abundance distribution.

\todo{Summary of secular evolution models which claim alpha-bimodality.} By incorporating stellar ``churning'' (changes in guiding-center radius) and ``blurring'' (changes in orbital eccentricity) as well as radial gas flows in a multi-ring model, \citet{schonrich_chemical_2009} successfully produced distinct high- and low-$\alpha$ sequences through secular processes alone; however, they failed to reproduce the overlap in metallicity between the two that would be a key finding of later surveys \citep[e.g.,][]{bensby_exploring_2014}. \citet{kubryk_evolution_2015} produce two parallel sequences in \aFe vs [Fe/H] by making a simple age cut to the results of their multi-zone GCE model, though because they do not present stellar \aFe distributions it is hard to determine whether their distributions are truly bimodal. In the model of \citet{sharma_chemical_2021}, a sharp transition in stellar \aFe for $8-12\Gyr$ old stars plus radial migration are the key ingredients for predicting a MW-like bimodality; however, their approach to the chemical evolution is not {\it ab initio}, meaning that instead of integrating the enrichment equations for their adopted star formation history, they simply assume a functional form for the abundance evolution over time \todo{(rewrite)}. \todo{Sharma basically says that it's possible to have a continuous star formation history and reproduce the $\alpha$-bimodality.} \citet{chen_chemical_2023} confirmed the findings of \citet{sharma_chemical_2021} in an {\it ab initio} multi-zone GCE model (with a two-phase ISM and radial gas flows but no outflows) and were able to produce a bimodal \aFe distribution; however, some discrepancies remain, including that the metallicity of the high-$\alpha$ sequence is too low and not extended enough. \citet{chen_chemical_2023} found that the abundance gap is caused by the simultaneous decline in SFR and \aFe. \citet{prantzos_origin_2023}.

@@

\begin{figure}
    \centering
    \includegraphics{figures/yield_outflow.pdf}
    \caption{The abundance evolution of three one-zone models with different yield sets and outflow mass-loading factors. Table \ref{tab:yields} presents the population-averaged yields for each model. The gray points with error bars indicate the mode of the APOGEE abundance distributions from the Solar neighborhood ($7\leq R_{\rm gal}<9\kpc$, $0\leq|z|<0.5\kpc$) in 1 Gyr-wide bins of the \citet{leung_variational_2023} age estimates.}
    \label{fig:yield-outflow}
\end{figure}

@@

The three models in Figure \ref{fig:yield-outflow} predict nearly identical evolution in [O/Fe] over the past 5 Gyr, and the trend in the data is similar apart from a $\sim0.05$ dex offset (which could be corrected by raising the SN Ia yield). The offset between the data and models grows between $\sim5-8\,{\rm Gyr}$, especially for the higher yields. Of the three, the \yZ{2} and \yZ{3} models most closely match the observed late-time age--metallicity relations, whereas the \yZ{1} model shows the best agreement with the observed [O/Fe] evolution. As the \yZ{2} and \yZ{3} models show generally similar behavior, we focus on the \yZ{1} and \yZ{2} yield sets for the remainder of this study.

@@

Most studies of the two-infall model assume the Milky Way has no significant mass-loaded outflows. Even in studies which do incorporate Galactic winds, the mass-loading is relatively weak \citep[e.g., $\eta\approx0.2$ in][]{palicio_analytic_2023}. To achieve a realistic radial metallicity gradient, many studies use a prescription for the infall timescale of the thin disk which increases linearly with radius \citep[e.g.,][]{chiappini_chemical_1997,romano_mass_2000}. Because we aim to study the effect of the yield assumptions on two-infall model predictions, we use mass-loaded outflows to control the final state of chemical evolution across the disk. As discussed by \citet{johnson_milky_2024}, evidence for or against outflows in Milky Way-type galaxies in simulations and observations is inconclusive.

\citet{weinberg_equilibrium_2017} showed that in the limit of continuous star formation, the ISM abundance approaches an equilibrium which is determined by the balance of yields, outflows, and star formation timescales. The mass-loading factor $\eta\equiv \dot\Sigma_{\rm out}/\dot\Sigma_\star$ required to reach equilibrium at Solar metallicity is
\begin{equation}
    \label{eq:equilibrium-eta}
    \eta_\odot = y_{\rm O}^{\rm CC} / Z_{\rm O,\odot} - 1 + r + \tau_\star / \tau_{\rm SFH},
\end{equation}
where $r=0.4$ is the instantaneous recycling parameter, $\tau_\star$ is the star formation efficiency timescale, and $\tau_{\rm SFH}$ is the star formation timescale. Equation \ref{eq:equilibrium-eta} informs our choice of $\eta$, but it is inaccurate in the two-infall case because of the bursty star formation history. Therefore, we tune the value of $\eta_\odot$ so that the model reaches $\mathOH=0.0$ by the end for each yield set, shown in Table \ref{tab:yields}.
% we find that if we adopt this prescription, models with $y/Z_\odot=1$ predict sub-Solar abundances at the present day because they have not yet reached their equilibrium value. 
\todo{This is not a constraint that most two-infall studies seem to care about.}

We adopt a prescription for the outflow mass-loading factor which increases exponentially with radius:
\begin{equation}
    \eta(R_{\rm gal}) = \eta_\odot \exp\Big(\frac{R_{\rm gal}-R_\odot}{R_\eta}\Big)
\end{equation}
where $R_\eta$ is the exponential outflow scale radius and $R_\odot=8\kpc$. As discussed by \citet{johnson_milky_2024}, an exponential trend in $\eta$ with $R_{\rm gal}$ produces a linear trend in [Fe/H] with $R_{\rm gal}$. We adopt $R_\eta=5$ kpc, a lower value than in \citet{johnson_milky_2024}, so that our $y/Z_\odot=1$ model produces a radial abundance gradient of $\nabla\mathOH_{\rm eq}\approx-0.06\,{\rm dex}\kpc^{-1}$ \todo{(citations)}.
% The exponential outflow scale radius $R_\eta$ sets the equilibrium abundance gradient $\nabla\mathOH_{\rm eq}$:
% \begin{equation}
%     R_\eta = -\frac{1}{\nabla\mathOH_{\rm eq} \times\ln(10)}.
% \end{equation}
% We adopt $R_\eta=7.2\kpc$ as our fiducial value, which corresponds to $\nabla\mathOH_{\rm eq}=-0.06$ dex kpc$^{-1}$.
% \todo{Motivate exponential scale radius.}

@@

The presence of outflows is not a necessary ingredient for the results of this study. We run a one-zone model with the fiducial parameters, $\eta=0$, and \yZ{0.8}, and find that it predicts similar abundance evolution and nearly identical stellar abundance distributions to the model with $\eta=0.2$ and \yZ{1}. If a model without mass-loaded outflows is desired, our multizone results for \yZ{1} should provide an adequate approximation.

@@

\begin{figure*}
    \centering
    \includegraphics{figures/spitoni_comparison.pdf}
    \caption{Chemical abundance tracks and distributions from one-zone models which use our fiducial parameters (solid curves) and the MCMC-derived parameters from \citet[][dashed curves]{spitoni_apogee_2021} at three different galactocentric radii. All models use the $y/Z_\odot=1$ yield set and corresponding outflow prescription (see Table \ref{tab:yields}). The time markers and marginal panels are the same as in Figure \ref{fig:twoinfall-parameters}. We also include a 2-D heatmap of the APOGEE stellar abundances in each panel for reference. APOGEE stars are restricted to (a) $2\leq R_{\rm gal}<6$ kpc, (b) $6\leq R_{\rm gal}<120$ kpc, and (c) $10\leq R_{\rm gal}<14$ kpc, and $0\leq |z|<2$ kpc in each panel.}
    \label{fig:spitoni-comparison}
\end{figure*}

@@

\begin{itemize}
    \item The ``turn-over'' in the evolution of [O/Fe] following the second infall produces a low-$\alpha$ sequence with a fundamentally different abundance structure than observed. A low yield set ($y/Z_\odot=1$) coupled with lower outflows, or pre-enrichment of the infalling gas, can bring the stellar [O/Fe] distributions more in line with the data.
    \item The large quantity of pristine gas accreted in the Solar neighborhood during the second infall phase rapidly dilutes the ISM metallicity by $\sim0.5$ dex. Models with a low yield set ($y/Z_\odot=1$) remain at sub-Solar metallicity until the present day, in stark contrast to the observed local age--metallicity relation. This issue can be mitigated with higher yields and outflows, but not by pre-enriched infall or radial migration.
    \item Our models predict that the MDF evolves to higher metallicity over time throughout the disk. This contrasts with the APOGEE data, which show very little change in the mode over the past $\sim6-8$ Gyr.
    \item The equilibrium scenario of chemical evolution, if correct, places stricter limits on the two-infall model than other evolutionary models.
\end{itemize}

>>>>

An explanation for the $\alpha$-bimodality has yet to be broadly accepted in the GCE community \todo{(reword)}. An $\alpha$-bimodality is not a universal feature in simulated Milky Way-mass galaxies \todo{(citations; also mention external galaxies?)}, so its presence and characteristics in our own galaxy may provide clues to its unique evolutionary history. GCE models that attempt to solve this problem generally fall into two camps. Some explain the $\alpha$-bimodality as a result of secular processes, such as the radial migration of stars and the inside-out growth of the disk \todo{(citations)}. Others argue that the two sequences point to a bursty star formation history, perhaps driven by multiple discrete accretion events \citep[e.g.,][]{chiappini_chemical_1997,mackereth_origin_2018,spitoni_beyond_2023} or a change in the star formation efficiency \citep[e.g.][]{conroy_birth_2022}.

% Summary of two-infall literature
The two-infall model of chemical evolution was proposed by \citet{chiappini_chemical_1997} to explain the origin of the high- and low-$\alpha$ disks. Though the model has been revised and refined since, the basic premise remains the same: the rate of gas infall onto the Galaxy is described by two consecutive, exponentially declining bursts. The relatively low infall rate between the two bursts leads to a hiatus in the star formation rate, allowing the gas abundance to evolve between the high- and low-$\alpha$ sequences while producing few stars in between. 
% By varying the timescale of the second infall, the model can produce inside-out disk growth and a radial abundance gradient.
The initial model of \citet{chiappini_chemical_1997} successfully reproduced the available abundance data at the time, which were largely confined to the Solar neighborhood.

@@

% \todo{Observational evidence other than $\alpha$-bimodality.} 
The chemical and kinematic separation of the high- and low-$\alpha$ disks remains the primary observational evidence behind the two-infall model. \citet{spitoni_remind_2024} argued that the observed gap between the sequences in \aFe, contrasted with their overlap in $[\alpha/{\rm H}]$, indicates a haitus in the star formation history, which is a natural consequence of the two-infall model. In different samples, \citet{nissen_high-precision_2020} and \citet{nataf_accurate_2024} observed multiple sequences in the local age--metallicity relation, which would naturally be explained by the two-infall scenario. Many two-infall studies have also reproduced the metallicity gradient, the local surface densities of stars and gas, and the local star formation and supernova rates \todo{(citations)}, although these observables can also be matched by other models \todo{(citations)}.
% \citet{nissen_high-precision_2020} measured abundances and estimated ages for nearby Solar-type stars and reported two sequences in the age--metallicity distribution which could be explained by the two-infall model \todo{(rewrite)}. \citet{nataf_accurate_2024} also observed multiple sequences in the age--metallicity relation in their sample of $\sim400,000$ local subgiants, although the break between them is not as clean as in \citet{nissen_high-precision_2020}.

% \todo{Outflows.} 
Most previous studies of the two-infall model do not include mass-loaded outflows. Some hydrodynamic simulations of Galactic fountains ejected by CC SNe have shown that ejected material falls back onto the disk on relatively short timescales \citep{spitoni_galactic_2008,spitoni_effects_2009} and close to their point of origin \citep{melioli_hydrodynamical_2008,melioli_hydrodynamical_2009}, suggesting the effect on GCE could be minimal. However, other simulations of MW-like galaxies with different feedback prescriptions do produce mass-loaded outflows \todo{(citations)}. Empirically, mass-loaded outflows have been observed in nearby starburst galaxies \todo{(citations)} and dwarf galaxies \todo{(citations)} but not MW-like systems due to current detection limits \todo{(citations)}. We adopt an {\it ad hoc} prescription for outflows as a function of radius in order to balance different yield sets and reproduce the radial metallicity gradient. \todo{Trim down, move some to methods.}

% \todo{Migration.} 
The two-infall model attempts to reproduce the full distribution of stellar abundances in the Solar neighborhood through a single, continuous evolutionary track. However, the current body of evidence suggests that many of the stars that make up the wings of the local metallicity distribution originate from elsewhere in the Galaxy. \citet{sellwood_radial_2002} first showed that transient spiral perturbations can induce large changes in the guiding radius of a star without kinematic heating, and it is now understood that the stars that make up the Solar neighborhood are drawn from a wide range of birth radii \citep[e.g.,][]{schonrich_chemical_2009,frankel_measuring_2018,lehmann_probing_2024}. Some studies have attempted to derive stellar birth radii \citep[e.g.,][]{ratcliffe_unveiling_2023,lu_there_2024}, though such an endeavor requires assumptions about the evolution of the Milky Way's radial metallicity gradient. While the strength and speed of radial migration in the disk are not precisely measured, it is clear that a single chemical evolution track need not explain the entirety of the local observed abundance distribution.

% \todo{Summary of secular evolution models which claim alpha-bimodality.} 
In contrast to the two-infall scenario, a number of studies have attempted to explain the $\alpha$-bimodality through purely secular processes. 
By incorporating stellar ``churning'' (changes in guiding-center radius) and ``blurring'' (changes in orbital eccentricity) as well as radial gas flows in a multi-ring model, \citet{schonrich_chemical_2009} successfully produced distinct high- and low-$\alpha$ sequences through secular processes alone; however, they failed to reproduce the overlap in metallicity between the two that would be a key finding of later surveys \citep[e.g.,][]{bensby_exploring_2014}. \citet{kubryk_evolution_2015} produce two parallel sequences in \aFe vs [Fe/H] by making a simple age cut to the results of their multi-zone GCE model, though because they do not present stellar \aFe distributions it is hard to determine whether their distributions are truly bimodal. In the model of \citet{sharma_chemical_2021}, a sharp transition in stellar \aFe for $8-12\Gyr$ old stars plus radial migration are the key ingredients for predicting a MW-like bimodality; however, their approach to the chemical evolution is not {\it ab initio}, meaning that instead of integrating the enrichment equations for their adopted star formation history, they simply assume a functional form for the abundance evolution over time \todo{(rewrite)}. \todo{Sharma basically says that it's possible to have a continuous star formation history and reproduce the $\alpha$-bimodality.} \citet{chen_chemical_2023} confirmed the findings of \citet{sharma_chemical_2021} in an {\it ab initio} multi-zone GCE model (with a two-phase ISM and radial gas flows but no outflows) and were able to produce a bimodal \aFe distribution; however, some discrepancies remain, including that the metallicity of the high-$\alpha$ sequence is too low and not extended enough. \citet{chen_chemical_2023} found that the abundance gap is caused by the simultaneous decline in SFR and \aFe. 
\todo{\citet{prantzos_origin_2023}.}
\citet{chen_recent_2025} argue that the double age--metallicity sequences observed by \citet{nissen_high-precision_2020} can be explained by a smooth star formation history with inside-out growth: the older sequence consists of stars which have migrated from the inner galaxy, where the star formation rate peaked early, while the younger sequence was formed locally. \todo{Trim this WAY down.}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{figures/yield_outflow.pdf}
    \caption{The abundance evolution of three one-zone models with different yield sets and outflow mass-loading factors. Table \ref{tab:yields} presents the population-averaged yields for each model. The gray points plot the abundances of APOGEE stars with NN ages from \citet{leung_variational_2023} from the Solar neighborhood ($7\leq R_{\rm gal}<9\kpc$, $0\leq|z|<0.5\kpc$). The black points with error bars indicate the mode of the abundance data in 1 Gyr-wide age bins, and the gray error bars along the bottom of each panel indicate the median age and abundance errors as a function of age.}
    \label{fig:yield-outflow}
\end{figure}

@@

The three models in Figure \ref{fig:yield-outflow} predict nearly identical evolution in [O/Fe] over the past 5 Gyr, and the trend in the data is similar apart from a $\sim0.05$ dex offset (which could be corrected by raising the SN Ia yield). The offset between the data and models grows between $\sim5-8\,{\rm Gyr}$, especially for the higher yields. Of the three, the \yZ{2} and \yZ{3} models most closely match the observed late-time age--metallicity relations, whereas the \yZ{1} model shows the best agreement with the observed [O/Fe] evolution. As the \yZ{2} and \yZ{3} models behave qualitatively similarly, we focus on the \yZ{1} and \yZ{2} yield sets for the remainder of this study.

@@

Mass-loaded outflows are a useful tool for scaling the endpoint of GCE models. \citet{weinberg_equilibrium_2017} showed that in the case of exponentially declining star formation, the O abundance approaches an equilibrium value at
\begin{equation}
    \label{eq:equilibrium}
    Z_{\rm O,eq} = \frac{y_{\rm O}^{\rm CC}}{1 + \eta - r - \tau_\star/\tau_{\rm SFH}},
\end{equation}
where $r=0.4$ is the instantaneous recycling parameter, $\tau_\star$ is the star formation efficiency timescale, $\tau_{\rm SFH}$ is the star formation timescale, and $\eta\equiv \dot\Sigma_{\rm out}/\dot\Sigma_\star$ is the outflow mass-loading factor. Equation \ref{eq:equilibrium} can be inverted to calculate the value of $\eta$ required to reach a desired $Z_{\rm O,eq}$ with a given yield, but it is inaccurate in the limit of zero accretion. We adopt values of $\eta_\odot=\eta(R=R_\odot)$ for each of our yield sets presented in Table \ref{tab:yields}. Models with lower yields do not achieve a steady-state abundance in time (see Figure \ref{fig:yield-outflow}); therefore, the values of $\eta_\odot$ for \yZ{1} and \yZ{2} are lower than would be suggested by Equation \ref{eq:equilibrium} in order to reach Solar metallicity at the end of the model.

Equation \ref{eq:equilibrium} suggests that one can achieve a different $Z_{\rm O,eq}$ in different regions of the Galaxy by adopting a spatially-varying prescription for $\eta$. In order to produce an exponentially declining radial metallicity gradient, we adopt a prescription for the outflow mass-loading factor which increases exponentially with radius:
\begin{equation}
    \eta(R_{\rm gal}) = \eta_\odot \exp\Big(\frac{R_{\rm gal}-R_\odot}{R_\eta}\Big)
\end{equation}
where $R_\eta$ is the exponential outflow scale radius and $R_\odot=8\kpc$. As discussed by \citet{johnson_milky_2024}, an exponential trend in $\eta$ with $R_{\rm gal}$ produces a linear trend in [O/H] with $R_{\rm gal}$. We adopt $R_\eta=5$ kpc, a lower value than in \citet{johnson_milky_2024}, so that our $y/Z_\odot=1$ model produces a radial abundance gradient of $\nabla\mathOH_{\rm eq}\approx-0.06\,{\rm dex}\kpc^{-1}$ \todo{(citations)}.

@@

Most previous studies of the two-infall model have assumed that the Milky Way has experienced no significant mass-loaded outflows. Even in studies which do incorporate Galactic winds, the mass-loading is relatively weak \citep[e.g., $\eta\approx0.2$ in][]{palicio_analytic_2023}. To achieve a realistic radial metallicity gradient, many studies adopt the yields of \citet{francois_evolution_2004} and use a prescription for the infall timescale of the thin disk which increases linearly with radius \citep[e.g.,][]{chiappini_chemical_1997,romano_mass_2000}. \todo{Additionally, many two-infall models reach a final metallicity higher than Solar. Citations for present-day gas abundance in the Solar neighborhood.}

As discussed by \citet{johnson_milky_2024}, evidence for or against outflows in Milky Way-type galaxies in simulations and observations is inconclusive. Because we aim to study the effect of the yield assumptions on two-infall model predictions, we use mass-loaded outflows to control the final state of chemical evolution across the disk. However, mass-loaded outflows are not a necessary ingredient for the results of this study. We find that a one-zone model with the fiducial parameters, $\eta=0$, and \yZ{0.8}, predicts a similar abundance evolution and nearly identical stellar abundance distributions to the model with $\eta=0.2$ and \yZ{1}. Therefore, our multizone models with \yZ{1} should predict similar behavior to a model without any mass-loaded outflows. %If a model without mass-loaded outflows is desired, our multizone results for \yZ{1} should provide an adequate approximation.

@@

\begin{figure*}
    \centering
    \includegraphics{figures/spitoni_comparison.pdf}
    \caption{Chemical abundance tracks and distributions from one-zone models which use our fiducial parameters (solid curves) and the MCMC-derived parameters from \citet[][dashed curves]{spitoni_apogee_2021} at three different galactocentric radii. All models use the $y/Z_\odot=1$ yield set and corresponding outflow prescription (see Table \ref{tab:yields}). The time markers and marginal panels are the same as in Figure \ref{fig:twoinfall-parameters}. We also include a 2-D heatmap of the APOGEE stellar abundances in each panel for reference. APOGEE stars are restricted to (a) $2\leq R_{\rm gal}<6$ kpc, (b) $6\leq R_{\rm gal}<10$ kpc, and (c) $10\leq R_{\rm gal}<14$ kpc, and $0\leq |z|<2$ kpc in each panel.}
    \label{fig:spitoni-comparison}
\end{figure*}

@@

\begin{itemize}
    \item The large quantity of pristine gas accreted in the Solar neighborhood during the second infall phase rapidly dilutes the ISM metallicity by $\sim0.5$ dex. Models with low nucleosynthetic yields (\yZ{1}) remain at sub-Solar metallicity until the present day, in stark contrast to the observed local age--metallicity relation. Models with higher yields and outflows approach the present-day metallicity more rapidly, while pre-enriched infall can reduce the magnitude of the dilution (but not eliminate it entirely). %This issue can be mitigated with higher yields and outflows, but not by pre-enriched infall or radial migration.
    \item The ``turn-over'' in the evolution of [O/Fe] following the second infall produces a double-peaked low-$\alpha$ sequence with a fundamentally different abundance structure than observed, especially for models with higher yields. A low yield set (\yZ{1}) coupled with lower outflows, or pre-enrichment of the infalling gas, can bring the stellar [O/Fe] distributions more in line with the data.
    \item For metal-rich stars, the two-infall model predicts a sharp divide in the stellar age distribution between the thick and thin disk populations. In contrast, the data show a smooth gradient between the oldest and youngest stars, with most of the metal-rich stars having intermediate ages.
    \item Our models predict that the MDF evolves to higher metallicity over time throughout the disk. This contrasts with the APOGEE data, which show very little change in the mode over the past $\sim6-8$ Gyr.
    \item The equilibrium scenario of chemical evolution, if correct, places stricter limits on the two-infall model than other evolutionary models.
\end{itemize}
